### 2018-07-16 99_Documentation/11_StabFem_BasicFunctionalities.tex

Looking inside the file \keys{Data.ff2m}, the header (i.e.  first four lines) is as follows :
\lstinputlisting[linerange={1-6,199}]{../EXAMPLE_Lshape/Data.ff2m}, 
meaning that this files contains a P1 mesh-organised field called 'T'.

@@

Execution of this step leads to the following :
\lstinputlisting[linerange={17-24}]{Lshape_ExecutionExample.txt}

@@

Execution of this step leads to the following :
\lstinputlisting[linerange={26-32}]{Lshape_ExecutionExample.txt}

@@

The line 4 explains the nature of the data which is contained in the file.
There can be as many data objects as you want organised in the order of your choice. The recognized types are currently as follows :
\begin{description}
\item{ \bf P1}  for mesh-structured data stored as P1 finite-elements
\footnote{P2 data is not yet supported, the solution is to convert everything to P1 before exportation.}  
\item{\bf P1c}  for mesh-structured {\em complex} data stored as P1 finite-elements
\item{\bf real} for real scalars,
\item{\bf complex} for complex scalars,
\item{\bf real.N} for real vectors of dimension N not associated to a mesh,
\item{\bf complex.N} for complex vectors of dimension N not associated to a mesh,
\item{\bf P1surf} for real data defined along a frontier of the mesh,
\item{\bf P1surfc} for complex data defined along a frontier of the mesh.
\end{description}

@@

to be continued...

>>>>

Looking inside the file \keys{Data.ff2m}, the header (i.e.  first four lines) is as follows :
\lstinputlisting[linerange={1-4}]{../EXAMPLE_Lshape/Data.ff2m}, 
meaning that this files contains a P1 mesh-organised field called 'T'.

@@

Execution of this step leads to the following :
\lstinputlisting[linerange={21-28}]{Lshape_ExecutionExample.txt}

@@

Execution of this step leads to the following :
\lstinputlisting[linerange={30-37}]{Lshape_ExecutionExample.txt}

@@

Line 2 contains a description string which is imported as field 'datadescription'.

Line 3 contains a series of property names and alphanumeric (string) values.

Line 4 explains the nature of the data which is contained in the file.
There can be as many data objects as you want organised in the order of your choice. The recognized types are currently as follows :
\begin{description}
\item{ \bf P1}  for mesh-structured data stored as P1 finite-elements
\footnote{P2 data is not yet supported, the solution is to convert everything to P1 before exportation.}  
\item{\bf P1c}  for mesh-structured {\em complex} data stored as P1 finite-elements
\item{\bf real} for real scalars,
\item{\bf complex} for complex scalars,
\item{\bf real.N} for real vectors of dimension N not associated to a mesh,
\item{\bf complex.N} for complex vectors of dimension N not associated to a mesh,
\item{\bf P1surf} for real data defined along a frontier of the mesh,
\item{\bf P1surfc} for complex data defined along a frontier of the mesh.
\end{description}

@@

Examination of the simple example here shows that the mesh generation produces four files (here all generated by the macro SF\_writemesh defined
in file Macros\_StabFem.edp)

\begin{itemize}
\item file \keys{mesh.txt} contains the mesh in the native FreeFem format. Namely, information about the vertices, the boundaries and the triangles. This mesh is imported in stabfem using importFFmesm.m , and it is also needed for subsequent Freefem++ programs.

\item file \keys{mesh.ff2m} contains informations about the mesh structure, to be imported by StabFem (it is read by importFFmesm.m)

\item file  \keys{SF\_Init.ff2m} contains informations about the mesh geometry, to be imported by StabFem as well  (it is also read by importFFmesm.m)

\item file \keys{SF\_geom.edp} contains definitions of case-dependent geometrical parameters which may be used by the FreeFem++ solvers.
This file is designed to be {\em included } in the header of the FreeFem++ solvers.
\end{itemize}

Note that files \keys{mesh.ff2m} and  \keys{SF\_Init.ff2m} may seem redundant... the difference is that  \keys{SF\_Init.ff2m} is created only once 
while  \keys{mesh.ff2m} is recreated each time the mesh is modified (adapted, splitted, etc...) .
